### 2013-01-19 edupar-13/410.tex
Remember to run "make" BEFORE committing.

The course has many learning objectives,
ranging from acquiring detailed factual knowledge about
hardware features
through practicing advanced cognitive processes
such as open-ended design.
%
Students study high-level concepts
such as
\shortversion{least privilege}{protection (least privilege, access control lists vs.\ capabilities)},
file-system internals,
and log-based storage.
%
Emphasis is placed on acquiring information from ``primary sources,''
including both manufacturer-provided hardware documentation
and a non-textbook technical-literature reading assignment.
%
Students begin with a ``blank slate'' rather than a
kernel-source template or an existing operating system,
so they must synthesize design requirements from multiple sources
and must
choose their own module boundaries and inter-module conventions.
%
\sortversion{The}{Due to the foundational nature of kernel code, the}
assignment design and grading encourage students to
think about corner cases, including resource exhaustion,
instead of being satisfied by
\shortversion{}{``the right basic idea''}
implementations that handle only auspicious situations.
%
Finally, most relevant to this work,
students gain substantial experience in
analyzing and writing lock-based multi-threaded code and
thread-synchronization objects.
They practice detecting and documenting deadlock and race conditions,
including both thread/thread concurrency and thread/interrupt concurrency.

>>>>

The course has many learning objectives,
ranging from acquiring detailed factual knowledge about
hardware features
through practicing advanced cognitive processes
such as open-ended design.
%
Students study high-level concepts
such as
\shortversion{least privilege}{protection (least privilege, access control lists vs.\ capabilities)},
file-system internals,
and log-based storage.
%
Emphasis is placed on acquiring information from ``primary sources,''
including both manufacturer-provided hardware documentation
and a non-textbook technical-literature reading assignment.
%
Students begin with a ``blank slate'' rather than a
kernel-source template or an existing operating system,
so they must synthesize design requirements from multiple sources
and must
choose their own module boundaries and inter-module conventions.
%
\shortversion{The}{Due to the foundational nature of kernel code, the}
assignment design and grading encourage students to
think about corner cases, including resource exhaustion,
instead of being satisfied by
\shortversion{}{``the right basic idea''}
implementations that handle only auspicious situations.
%
Finally, most relevant to this work,
students gain substantial experience in
analyzing and writing lock-based multi-threaded code and
thread-synchronization objects.
They practice detecting and documenting deadlock and race conditions,
including both thread/thread concurrency and thread/interrupt concurrency.

### 2013-01-19 edupar-13/intro.tex
Remember to run "make" BEFORE committing.

In comparison with other educational kernel projects,
% such as Pintos~\cite{pintos} and Xv6~\cite{xv6},
Pebbles focuses more on ground-up design than on teaching a broad feature set.
% Pebbles allows students to design and implement their systems ``from the ground up.''
At Stanford, students build kernels following the Pintos architecture~\cite{pintos}, and at MIT, following the Xv6/JOS architecture~\cite{xv6}.
In both courses, student kernels support multiprocessor execution;
however, students are also supplied with starter code that already implements thread creation/destruction, context switching, and locking primitives.
In 15-410, we provide starter code for the machine boot sequence and for a minimal C library (\x{printf()}, \xmalloc()}), leaving students to design threading and scheduling primitives from scratch.

>>>>

In comparison with other educational kernel projects,
% such as Pintos~\cite{pintos} and Xv6~\cite{xv6},
Pebbles focuses more on ground-up design than on teaching a broad feature set.
% Pebbles allows students to design and implement their systems ``from the ground up.''
At Stanford, students build kernels following the Pintos architecture~\cite{pintos}, and at MIT, following the Xv6/JOS architecture~\cite{xv6}.
In both courses, student kernels support multiprocessor execution;
however, students are also supplied with starter code that already implements thread creation/destruction, context switching, and locking primitives.
In 15-410, we provide starter code for the machine boot sequence and for a minimal C library (\x{printf()}, \x{malloc()}), leaving students to design threading and scheduling primitives from scratch.
